### 2013-03-24 mcmc.tex
tweaks, notes to selves re other methods

When the sampling $\setof{x_k}_{k=1}^K$ is of one of these badly
normalized functions $f(x)$---as it usually will be---the
sampling-approximation expectation values are the expectation values
under the properly-normalized corresponding pdf, even though you might
never \emph{learn that normalization}.
When we run MCMC sampling on $f(x)$, a function which differs from a
pdf $p(x)$ by some unknown normalization constant, then the sampling
permits computation of the following kinds of quantities:
\begin{eqnarray}
E[q] &\equiv& \frac{\int q(x)\,f(x)\,\dd x}{\int f(x)\,\dd x}
\\
E[q] &\approx& \frac{1}{K}\,\sum_{k=1}^K q(x_k)
\quad .
\end{eqnarray}
That is, the sampling can be constructed (as we will show below) from
$f(x)$ directly, and it permits you to compute expectation values
without ever requiring you to integrate either the numerator or the
denominator integrals, both of which are generally intractable.\note{As
  we will
  see, the intractability comes from various directions, but one is
  that the dimension of $x$ gets large in most realistic situations.
  Another is that the support of $p(x)$ tends to be, in normal
  inference situations, \emph{far smaller} than the full domain of
  $x$.
  That is, the pdf is at or very close to zero over all but some tiny
  and very hard-to-find part of the space.}

@@

% *********** BJB
% I suggest partitioning the discussion of different methods into the following
% two categories:
%
%  i) Methods for getting around the target distribution
% ii) Methods that change the target distribution to something
% other than the posterior pdf, to help the sampling somehow
%
% i) Would include things like M-H, the stretch move,
% Hamiltonian, slice sampling (maybe skip the latter)
% ii) would include things like annealing and Nested Sampling

@@

...How does the stretch move work?

...Why is the stretch move useful?

@@

>>>>

When the sampling $\setof{x_k}_{k=1}^K$ is of one of these badly
normalized functions $f(x)$---as it usually will be---the
sampling-approximation expectation values are the expectation values
under the properly-normalized corresponding pdf, even though you might
never \emph{learn that normalization}.
When we run MCMC sampling on $f(x)$, a function which differs from a
pdf $p(x)$ by some unknown normalization constant, then the sampling
permits computation of the following kinds of quantities:
\begin{eqnarray}
E[q] &\equiv& \frac{\int q(x)\,f(x)\,\dd x}{\int f(x)\,\dd x}
\\
E[q] &\approx& \frac{1}{K}\,\sum_{k=1}^K q(x_k)
\quad .
\end{eqnarray}
That is, the sampling can be constructed (as we will show below) from
$f(x)$ directly, and it permits you to compute expectation values
without ever requiring you to integrate either the numerator integral
or the denominator integral, both of which are generally
intractable.\note{As we will
  see, the intractability comes from various directions, but one is
  that the dimension of $x$ gets large in most realistic situations.
  Another is that the support of $p(x)$ tends to be, in normal
  inference situations, \emph{far smaller} than the full domain of
  $x$.
  That is, the pdf is at or very close to zero over all but some tiny
  and very hard-to-find part of the space.}

@@

...Why everyone reading this document should stop here and JUST FREAKIN' CODE THIS UP.

% *********** BJB talking:
% I suggest partitioning the discussion of different methods into the following
% two categories:
%
%  i) Methods for getting around the target distribution
% ii) Methods that change the target distribution to something
% other than the posterior pdf, to help the sampling somehow
%
% i) Would include things like M-H, the stretch move,
% Hamiltonian, slice sampling (maybe skip the latter)
% ii) would include things like annealing and Nested Sampling

@@

%%%% Hogg talking:
% DFM: In this section, I think we should just summarize the other
% methods, not describe them in detail.  Then we can cite the relevant
% papers for the enthusiastic.

...What, briefly, is the stretch move, and why is it useful?

@@

...What, briefly, is reversible-jump, and why is it useful?
